Kindly Bent to Free Us

### 2018-11-16 kindly/infer/infer.tex
minor tweaks for readability

\begin{figure}[h]
  \centering
  \begin{align*}
    C ::=&\ \Cleq{\tau_1}{\tau_2}\ |\ \Cleq{k_1}{k_2}\ |\ C_1 \Cand C_2\ |\ \Cproj{\alpha}{C}
  \end{align*}
  \caption{The constraint language}
  \label{grammar:constraint}
\end{figure}

\begin{figure*}[h]
  \input{infer/entails}
  \caption{Base entailment rules -- $\entail{C}{D}$ }
  \label{rules:entail}
\end{figure*}

@@

In order to determine if a variable is used in an affine manner, we must track
it's uses and the associated kinds. For instance, in the expression
$(x,x)$, $x$ is used twice. If $x$ is of type $\tau$, which is of kind $k$,
we must add the constraint $\Cleq{k}{\kun}$. In order to record uses and kinds,
our type inference relation will return a ``usage map'', noted $\Sv$,
which associates each variable to a list of kinds corresponding to each use site
of the variable.
We note $\Sone{x}{k_1,\dots,k_n}$ the singleton usage map.
Common operations on usages maps are defined in \cref{op:usgmap}. We define
regular set operations such as union
($\Sv\cup\Sv'$) and intersection ($\Sv\cap\Sv'$), along
with constraint creation $\Cleq{\Sv}{k_0}$ which indicates that all the kinds
presents in the usage map $\Sv$ are constrained by the kind $k_0$.
These operations corresponds roughly to the various parts of the join
operator on sets $\esplit{}{}$.

\begin{figure}[h]\centering
\begin{align*}
  \Sv\cap\Sv'
  &= \left\{ x \to l,l'
    \mid \Sone{x}{l}\in\Sv \text{ and } \Sone{x}{l'}\in\Sv' \right\} \\
  \Sv\cup\Sv'
  &= \Sv\cap\Sv' \sqcup
    (\Sv\Sdel{x' \mid x'\in\Sv'}) \sqcup
    (\Sv'\Sdel{x \mid x\in\Sv})
  &\text{where $\sqcup$ is the disjoint union}\\
  \Cleq{\Sv}{k_0}
  &= \bigwedge_{\Sone{x}{l_x}\in\Sv} \bigwedge_{k\in l_x} \Cleq{k}{k_0}
\end{align*}
\caption{Operation on usage maps $\Sv$}
\label{op:usgmap}
\end{figure}

>>>>

\begin{figure}[tp]
  \centering
  \begin{align*}
    C ::=&\ \Cleq{\tau_1}{\tau_2}\ |\ \Cleq{k_1}{k_2}\ |\ C_1 \Cand C_2\ |\ \Cproj{\alpha}{C}
  \end{align*}
  \caption{The constraint language}
  \label{grammar:constraint}
\end{figure}

\begin{figure*}[tp]
  \input{infer/entails}
  \caption{Base entailment rules -- $\entail{C}{D}$ }
  \label{rules:entail}
\end{figure*}

@@

In order to determine if a variable is used in an affine manner, we must track
its uses and the associated kinds. For instance, in the expression
$(x,x)$, $x$ is used twice. If $x$ is of type $\tau$, which is of kind $k$,
we must add the constraint $\Cleq{k}{\kun}$. In order to record uses and kinds,
our type inference relation will return a ``usage map'', noted $\Sv$,
which associates each variable to a list of kinds corresponding to each use site
of the variable.
We note $\Sone{x}{k_1,\dots,k_n}$ the singleton usage map.
Common operations on usage maps are defined in \cref{op:usgmap}. We define
regular set operations such as union
($\Sv\cup\Sv'$) and intersection ($\Sv\cap\Sv'$), along
with constraint creation $\Cleq{\Sv}{k_0}$ which indicates that all the kinds
presents in the usage map $\Sv$ are constrained by the kind $k_0$.
These operations corresponds roughly to the various parts of the join
operator on sets $\esplit{}{}$.

\begin{figure}[tp]\centering
\begin{align*}
  \Sv\cap\Sv'
  &= \left\{ x \to l,l'
    \mid \Sone{x}{l}\in\Sv \text{ and } \Sone{x}{l'}\in\Sv' \right\} \\
  \Sv\cup\Sv'
  &= \Sv\cap\Sv' \sqcup
    (\Sv\Sdel{x' \mid x'\in\Sv'}) \sqcup
    (\Sv'\Sdel{x \mid x\in\Sv})
  &\text{where $\sqcup$ is the disjoint union}\\
  \Cleq{\Sv}{k_0}
  &= \bigwedge_{\Sone{x}{l_x}\in\Sv} \bigwedge_{k\in l_x} \Cleq{k}{k_0}
\end{align*}
\caption{Operation on usage maps $\Sv$}
\label{op:usgmap}
\end{figure}
